---
title: "qacReg for Logistic Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{qacReg for Logistic Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, message=FALSE, warning=FALSE,
  comment = "#>"
)
```

In this analysis, we'll develop a model for predicting births by caesarian from patient characteristics uing the `caesarian` data frame.

Model fitting is normally an iterative process. We'll skip this to keep things simple.

### Fit the model

```{r setup}
library(qacReg)
data(caesarian)

fit <- glm(caesarian ~ ., family = binomial, data = caesarian)

# or
# fit <- regress(caesarian ~ ., data = caesarian)
```

### Examine the model

```{r}
info(fit)
```


### Perform regression diagnostics

```{r}
diagnostics(fit)
```


### Visualize the model parameters

```{r}
forest_plot(fit)
```

```{r, fig.height=7}
me_plots(fit)
```


### Evaluate variable importance

```{r}
relimp(fit)
```


### Assess  predictive performance

```{r}
performance(fit)
```

### Additional output

#### ROC Plot

```{r}
pred <- predict(fit, caesarian, type="response")
roc_plot(caesarian$caesarian, pred, positive="yes")

```

#### Lift and Gain Charts

```{r}
lift_plot(caesarian$caesarian, pred, positive="yes")
```

