---
title: "qacReg for Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{qacReg for Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, message=FALSE, warning=FALSE,
  comment = "#>"
)
```

This short vignette demonstrates many of the functions in the **qacReg** package. In this analysis, we'll develop a model for predicting fuel efficiency from car characteristics using the `auto_mpg` data frame.

Model fitting is normally an iterative process. We'll skip this to keep things simple.

# Fit the model
```{r setup}
library(qacReg)
data(auto_mpg)

fit <- lm(mpg ~ ., data = auto_mpg)

# or
# fit <- regress(mpg ~ ., data = auto_mpg)
```

# Examine the model

```{r}
info(fit)
```


# Perform regression diagnostics

```{r}
diagnostics(fit)
```


# Visual the model parameters

```{r}
ggforestPlot(fit)
```

```{r, fig.height=7}
plots(fit)
```


# Evaluate variable importance

```{r}
relimp(fit)
```


# Assess model predictive performance

```{r}
performance(fit)
```


